TRITON: Globally Consistent Sim-to-Real Transfer

### 2022-06-06 CORL/example.tex
Changed caption for texture realism loss
Started texture reality and unprojection consistency sections

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/unprojection_consistency_loss.pdf}
	\end{center}
	\caption{
		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
		we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
		If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
		We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$, then averaging the result.
		When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
		Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
	}
	\label{fig:unprojection_consistency_loss}
\end{figure}

@@

\subsection{Texture Realism Loss}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
	\end{center}
	\caption{
		The neural texture looks more realistic with texture realism loss enabled.
	}
	\label{fig:texture_realism_ablation}
\end{figure}

@@

We use L2 and MSSSIM losses to do this.

@@

@@

(Give theoretical explation)

>>>>

%%%%%%%%%%%%BIG TODO::::
%%%%%% MAKE BATCH SIZE N INSTEAD OF B - B is a domain!

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/unprojection_consistency_loss.pdf}
	\end{center}
	\caption{
		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
		The Unprojection Mean and Reprojection nodes are not used in any losses, and help to illustrate the next section \ref{sec:texture_realism_loss}.
		% After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
		% we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
		% If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
		% We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$, then averaging the result.
		% When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
		% Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
	}
	\label{fig:unprojection_consistency_loss}
\end{figure}

Heres the equation for unprojection consistency loss:
$\ell_{UC} = \mu\left(\sigma\left(u\right)_{1 \dots L}\right)$

@@

\subsection{Texture Realism Loss}
\label{sec:texture_realism_loss}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
	\end{center}
	\caption{
		The neural texture looks more realistic with texture realism loss enabled. Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments. 
	}
	\label{fig:texture_realism_ablation}
\end{figure}

@@

We use l2 and msssim losses to do this.

@@

Texture realism loss equation:
$L_{TR}=L_{TR_{l2}}+L_{TR_{msssim}}$
where 
$L_{TR_{msssim}} = -msssim(\pi,\hat{p})$ and
$L_{TR_{l2}} = \frac{
	\sum\limits_{i=1}^B {
	   %  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
	   \left( \pi-\hat{p}  \right)^2
		} 
   }
   {B}$

@@

(Give theoretical explation)
$
\ell_{UC} = 
\
\
\mu\left(\sigma\left(u_{1\dots B,\ 1\dots L}\right)_{1 \dots L}\right) = 
\sqrt{
\frac{
	 \sum\limits_{i=1}^B {
		%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
		\left( \hat{p}-\bar{p}  \right)^2
		 } 
	}
	{B}
}
$
Using $\bar{p}$ from figure \ref{fig:unprojection_consistency_loss}

Becuase $\bar{p}$ is created from the average recovered texturs of $\hat{p}$, $\bar{p} \approx \hat{p}$.

Becuse of texture realism loss, $\pi \approx \hat{p}$.

Therefore, $\bar{p} \approx \hat{p} \approx \pi$

% The l2 component of the texture realism loss equation:
% $ \
% \
% \
% \
% \ \ell_{TR_{l2}}=\sum\limits_{i=1}^B {
% 	%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
% 	\left( \pi-\hat{p}  \right)^2
% 	 } 
% $

Substituting one projected texture for another, aka $\pi$ for $\bar{p}$, we get 
$ \
\
\
\
\ \ell_{TR_{l2}}
\approx
\frac{\sum\limits_{i=1}^B {
	%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
	\left( \hat{p}-\pi  \right)^2
	 }}{B} = \ell_{UC}^2
$
